---
title: "My Assignment"
description: |
  Mini Challenge 2
author:
  - name: Rhoda Tong
    url: www.smu.edu.sg
date: 07-25-2021
output:
  distill::distill_article:
    self_contained: false
    toc: true

preview: Images/TruckRoutesWkTwo.jpg
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE, fig.retina = 3)
```

```{r Installing Loading Reqd Libraries, include=FALSE}

packages = c('DT','tidyverse', 'ggiraph', 'plotly', 'lubridate', 'naniar','stringr','dplyr','ggstance','ggpubr','hms','data.table','raster','sf','tmap','clock','rgdal','tibbletime','scales','knitr')

for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```


# Background

Since 20 years ago, GASTech has been operating a natural gas production site in the island country of Kronos. The business has been profitable, and the company has also developed close relationships with the Kronos Government. In January 2014, following GASTech's initial public offering listing, several GASTech employees has gone missing. An organization known as Protectors of Kronos (POK) is suspected in these cases of missing persons, as GASTech's business moves had not been too environmentally friendly. A thorough investigation is to be carried out by the law enforcers of Kronos and Tethys to break this case.

Information and data pertaining to the whereabouts of company cars, purchases made by employees in local stores have been provided to the law enforcers. We shall use visual analytics to sense-make this data to facilitate the investigation. 

This would be done as a sub-component which would eventually feed into an interactive Shiny app for the use of the law enforcers, together with other sub-components covered by my project group mates. The objective of this assignment is to explore what the insights are and how they can be brought out from the depths of this dataset to aid in the investigation.

